%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins

\name{Edouard Swiac} % Your name
\address{415.513.8306 | 1660 Mason street apt. 3 \\ San Francisco CA 94133} % Your address
\address{\href{mailto:edouard.swiac@gmail.com}{edouard.swiac@gmail.com} | \href{https://github.com/edouardswiac}{github.com/edouardswiac}} % Your phone number and email
\begin{document}



%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Work experience}

\begin{rSubsection}{Hotwire.com (an Expedia, Inc company)}{Since April 2012}{Software engineer}{San Francisco, CA}
\item Platform engineering team of 3, working closely with software architects using the Kanban method
\item Team successfully extracted and modularized the business rules engine (ILOG) from the monolithic Hotwire code base to a modular maven/Spring 3 decoupled service.
\item Led the continuous integration effort of business pricing rules' regression testing, from manual testing done by Revenue Management team to an automated job in Jenkins.
\item Developed a modular JMX client used by monitoring systems in production and QA environments.
\item Proposed and designed a solution to generate and store Hotwire search data (air/hotel/car queries) in a NoSQL database using BDD, AOP and MongoDB.
\item Worked with Java 6, Spring 3 (DI, Remoting), maven 3, MongoDB, Jenkins
\end{rSubsection}

\begin{rSubsection}{2600hz}{April 2011 - April 2012}{Software engineer}{San Francisco, CA}
\item Various contributions to major features (voicemail, hot desk, call flows) of the open-source, carrier-grade VoIP platform Kazoo.
\item Built REST APIs on top of CouchDB and respecting REST principles.
\item Developed integration with Microsoft Lync Server (outbound calling, call forwarding, AMQP bus communications).
\item Several contributions to a server deployment tool and a gem to consume the platform's services.
\item Worked with Erlang/OTP, CouchDB, git, ruby.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Agendize}{November 2010 - March 2011}{Software engineer - contractor}{Montreal, CA}
\item Partial implementation of RFC 4791 (CalDav) to add synchronization to a calendar feature.
\item Worked with Java.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Sellermania}{July 2010 - October 2010}{Software engineer intern}{Paris, France}
\item Design and development of an heuristic to weight the pricing strategy of 20 millions items sold on Amazon FR, UK and DE.
\item Worked with Java, Hibernate 3, MySQL.
\end{rSubsection}

\begin{rSubsection}{Usine 23}{July 2008 - January 2010}{Software engineer intern}{Paris, France}
\item Built a PHP middleware to connect several heterogenous ecommerce APIs to the company PHP backend. It performed listings export, orders import, data curation and sales synchronization.
\item Wrote core business and service classes for the backend. Architected the foundations of the company's internal PHP framework.
\item Worked with PHP 5.2, MySQL.
\end{rSubsection}

\end{rSection}

\newpage
%----------------------------------------------------------------------------------------
%   EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf SUPINFO San Francisco, CA} \hfill {\em November 2011} \\
M.S. in Computer Science \\
Thesis: "Integration of software components in an heterogeneous distributed environment" \\

{\bf Dominican University of California, San Rafael CA} \hfill {\em November 2011} \\
Certificate in Management and Marketing of IT \\

{\bf SUPINFO Paris, France} \hfill {\em November 2010} \\
B.S. in Computer Science \\

\end{rSection}

%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Technical skills}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Computer Languages & Java (Spring/Maven), Python, Erlang/OTP, PHP (Zend certified)\\
Web development & HTML5/CSS3, jQuery. Good sense of design and UI\\
Protocols \& APIs & XML, JSON, HTTP+REST, AMQP \\
Databases & MySQL, PostgreSQL, MongoDB, Redis \\
Other & Perforce/git, Eclipse/Vim. Linux/Mac OS. TDD/BDD. Agile methods.
\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Personal software projects}
\item Creator of \url{http://linkstash.net}, a short-term bookmarking web app that runs with Python/Flask, Redis and Heroku.
\item Founder of \url{http://musicpad.me}, a platform for musicians and music teachers to manage and share their repertoire's music sheets and tablatures. In development.
\item Submitted French translation of PHP documentation (SVN \#290561).
\item Arduino pet project: remote controllable heater.
\end{rSection}

\begin{rSection}{Interests}
\item \textbf{Sports} Avid runner and soccer player. Beginner at boxing, interested in golf.
\item \textbf{Music} Guitar and bass player for over 7 years. Attending music school. Playing in a band.
\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
